A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-11 analysis.tex
Adding comments and references
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@613 ccdd05d5-56c1-461a-bf98-85f6876523b4
Add comment on flops
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@614 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{It would be good to illustrate the layout of this particular template bank: masses spanned, time slice layout \dots}
\begin{table}[!h]
\caption{Operation counts per sample for six different detection methods.  The operation counts for \textsc{lloid} assume a reconstruction duty cycle of 5\%.  Note that the \textsc{fir} method with \textsc{lloid} is almost 10 times faster than the conventional \textsc{fft} method, despite having substantially lower latency.}
\begin{center}
\input{flop_budget}
\end{center}
\end{table}

>>>>

\editorial{It would be good to illustrate the layout of this particular template bank: masses spanned, time slice layout \dots}
\editorial{Drew: I think this should say the FFT version of LLOID is almost 10 times faster than the conventional FFT method.}
\editorial{Drew: It would be good to have these numbers for with SVD only, with SVD + TIME SLICES, and SVD+COMPDETSTAT. Then we can show which combination allows you to save time.}
\begin{table}[!h]
\caption{Operation counts per sample for six different detection methods.  The operation counts for \textsc{lloid} assume a reconstruction duty cycle of 5\%.  Note that the \textsc{fir} method with \textsc{lloid} is almost 10 times faster than the conventional \textsc{fft} method, despite having substantially lower latency.}
\begin{center}
\input{flop_budget}
\end{center}
\end{table}
